Ranking Stability

### 2021-08-10 output_scripts/investigate_rankings.Rmd
update sim ests being used

# Ranking and Events

We first modify the priors from the C-MMHP model which leads to
much improved MCMC performance.

We want to look at the relationship between the inferred variability
of the ranking and the number of interactions a given animal is involved in.

We plot the inferred ranks arranged by decreasing number
of total interactions for all 4 of the comparison models, as in Fig6a.

```{r plot-rank-total-interactions, eval=FALSE}
 for(current_cohort in 1:10) {
   clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
   load(paste(data_path,
              cohort_names[current_cohort],
              "/cohort_mmhp_stan_result_",
              cohort_names[current_cohort],
              ".RData",
              sep = ""
              ))
   total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count)
   f_ranks <- paste("f[", order(total_inter, decreasing = TRUE),
                    "]", sep = "")
   f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>%
   pivot_longer(everything())
   f_draws$name <- factor(f_draws$name, levels = f_ranks)
   plot_f <- f_draws %>%
   ggplot(aes(name, value)) +
   geom_boxplot() +
   labs(title = paste("Cohort ", current_cohort, sep = ""),
        subtitle = "Ordered by total interactions")
   print(plot_f)
 }
```

@@

>>>>

<!-- # Ranking and Events -->

<!-- We first modify the priors from the C-MMHP model which leads to -->
<!-- much improved MCMC performance. -->

<!-- We want to look at the relationship between the inferred variability -->
<!-- of the ranking and the number of interactions a given animal is involved in. -->

<!-- We plot the inferred ranks arranged by decreasing number -->
<!-- of total interactions for all 4 of the comparison models, as in Fig6a. -->

<!-- ```{r plot-rank-total-interactions, eval=FALSE} -->
<!--  for(current_cohort in 1:10) { -->
<!--    clean_data <- cleanData(full_data[[cohort_names[current_cohort]]]) -->
<!--    load(paste(data_path, -->
<!--               cohort_names[current_cohort], -->
<!--               "/cohort_mmhp_stan_result_", -->
<!--               cohort_names[current_cohort], -->
<!--               ".RData", -->
<!--               sep = "" -->
<!--               )) -->
<!--    total_inter <- rowSums(clean_data$N_count) + colSums(clean_data$N_count) -->
<!--    f_ranks <- paste("f[", order(total_inter, decreasing = TRUE), -->
<!--                     "]", sep = "") -->
<!--    f_draws <- sim_cohort_mmhp %>% select(starts_with("f")) %>% -->
<!--    pivot_longer(everything()) -->
<!--    f_draws$name <- factor(f_draws$name, levels = f_ranks) -->
<!--    plot_f <- f_draws %>% -->
<!--    ggplot(aes(name, value)) + -->
<!--    geom_boxplot() + -->
<!--    labs(title = paste("Cohort ", current_cohort, sep = ""), -->
<!--         subtitle = "Ordered by total interactions") -->
<!--    print(plot_f) -->
<!--  } -->
<!-- ``` -->

@@

# Examine new simulation results

```{r inferred-rankings}
sim_data_path <- here("output",
                      "revisions",
                      "lapl_check",
                      "real_recov", "/")

sim_files <- list.files(sim_data_path, pattern = "sim_model3_fit")

num_nodes <- 12

cohort_est <- readRDS(here("output", "sim_ests.RDS"))

f_vec <- mean_values %>% 
  pivot_wider(names_from = variable, values_from = mean) %>% 
  select(starts_with("f")) %>% 
  as.numeric()

sim_ranks_mean <- tibble()
sim_ranks <- tibble()

model_colors <- col_df %>%
  filter(method %in% c(
    "C-HP",
    "C-DCHP", "C-MMHP"
  )) %>%
  pull(cols)

for(curr_sim in seq_along(sim_files)) {
  load(paste0(sim_data_path,
              sim_files[curr_sim]))

  f_m1 <- sim_model3_stan_sim1 %>% select(starts_with("f"))
  m1_ranks <- apply(f_m1, 2, mean)

  f_m1_sims <- f_m1 %>% 
    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
    pivot_longer(everything(),
                 names_to = "node",
                 values_to = "rank")
  f_m1_sims$model <- "C-HP"

  f_m2 <- sim_model3_stan_sim2 %>% select(starts_with("f"))
  m2_ranks <- apply(f_m2, 2, mean)

  f_m2_sims <- f_m2 %>% 
    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
    pivot_longer(everything(),
                 names_to = "node",
                 values_to = "rank")

  f_m2_sims$model <- "C-DCHP"

  f_m3 <- sim_model3_stan_sim3 %>% select(starts_with("f"))
  m3_ranks <- apply(f_m3, 2, mean)

  f_m3_sims <- f_m3 %>% 
    rename_with(~gsub("f[", "", .x, fixed = TRUE)) %>% 
    rename_with(~gsub("]", "", .x, fixed = TRUE)) %>% 
    pivot_longer(everything(),
                 names_to = "node",
                 values_to = "rank")

  f_m3_sims$model <- "C-MMHP"

  curr_mean_ranks <- tibble(model = c(rep("C-HP", num_nodes),
                                 rep("C-DCHP", num_nodes),
                                 rep("C-MMHP", num_nodes)),
                       ranks = c(m1_ranks,
                                 m2_ranks,
                                 m3_ranks),
                       node = rep(1:num_nodes, 3),
                       true_rank = rep(f_vec, 3),
                       sim_id = curr_sim)
  sim_ranks_mean <- sim_ranks_mean %>% 
    bind_rows(curr_mean_ranks)

  sim_ranks <- sim_ranks %>% 
    bind_rows(f_m1_sims, f_m2_sims, f_m3_sims)

}

sim_ranks$node <- factor(sim_ranks$node, levels = 1:num_nodes)
sim_ranks_mean$node <- factor(sim_ranks_mean$node, levels = 1:num_nodes)

# sim_ranks$node

sim_ranks_mean$model <- factor(sim_ranks_mean$model, 
                               levels = c( "C-HP", "C-DCHP", "C-MMHP"))

mean_sims <- sim_ranks_mean %>% 
  left_join(col_df, by = c("model" = "method"))

mean_sims$model <- factor(mean_sims$model, levels = c("C-HP", "C-DCHP",
                                                      "C-MMHP"))

true_ranks <- tibble(node = rep(1:num_nodes,3),
                     true_rank = rep(f_vec,3),
                     model = c(rep("C-HP", num_nodes),
                               rep("C-DCHP", num_nodes),
                               rep("C-MMHP", num_nodes)))
true_ranks$node <- factor(true_ranks$node, levels = 1:num_nodes)

true_ranks$model <- factor(true_ranks$model, 
                           levels = c("C-HP", "C-DCHP","C-MMHP"))

mean_sims %>% 
  # filter(model == "C-MMHP") %>% 
  ggplot(aes(node, ranks, fill = model)) + 
  geom_boxplot(show.legend = FALSE) +
  scale_fill_manual(values = model_colors, guide = FALSE) +
  # geom_point(aes(node, true_rank, colour = "red")) +
  ylim(c(0,1)) +
  labs(title = "(a)",
       subtitle = "Mean rank from each simulation", 
       y = "Posterior Mean Rank", x = "Node") +
  facet_wrap(~model) +
  geom_point(data = true_ranks,
             aes(node, true_rank, colour = "True Value")) +
  scale_shape_discrete(name = "True Value") +
  theme_minimal() +
  theme(legend.title = element_blank(),
        legend.position = "bottom",
        plot.title = element_text(hjust = 0.5, size = 26),
        text = element_text(size = 18),
        legend.text = element_text(size = 18))

```

What about the recovery of the other parameters?

```{r eta_recovery}

eta_ests <- tibble()

for(curr_sim in seq_along(sim_files)) {
  load(paste0(sim_data_path,
              sim_files[curr_sim]))

  eta_m1 <- sim_model3_stan_sim1 %>% 
    select(starts_with("eta")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = mean(value)) %>% 
    mutate(model = "C-HP")

  eta_m2 <- sim_model3_stan_sim2 %>%
    select(starts_with("eta")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = mean(value)) %>% 
    mutate(model = "C-DCHP")

  eta_m3 <- sim_model3_stan_sim3 %>%
    select(starts_with("eta")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(mean_est = mean(value)) %>% 
    mutate(model = "C-MMHP")

  curr_sim_ests <- bind_rows(eta_m1,
                             eta_m2,
                             eta_m3)

  eta_ests <- eta_ests %>% 
    bind_rows(curr_sim_ests)

}

eta_ests$model <- factor(eta_ests$model, levels = c("C-HP",
                                                    "C-DCHP",
                                                    "C-MMHP"))

tru_values <- tibble(name = c("eta_1", "eta_2", "eta_3"),
                     mean_est = c(object_par$sim_eta_1,
                                  object_par$sim_eta_2,
                                  object_par$sim_eta_3))

eta_ests %>% 
  ggplot(aes(name, mean_est)) +
  geom_boxplot(aes(fill = model)) +
  geom_hline(mapping = aes(yintercept = mean_est),
             tru_values, colour = "red") +
  facet_wrap(~name)

```
